NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-16 paper/Chapters/Chapter3.tex
results with survery regression updated

\textbf{Table \ref{tab:tab1hypetension}} presents the characteristics of men and women participants in the NDNS RP 2008/09-15/16 by hypertension status. The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women. Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, WC, and prevalence of diabetes (\textit{p} < 0.01). Differences were also found for carbohydrate eating patterns defined previously, total energy intake, as well as total carbohydrate intake (\textit{p} < 0.001). No difference was found among either men or women for geographic location, and ethnicity. Strong evidence of difference was found in women for average household income (32741.5 \textsterling/year in non-hypertensive vs. 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men.

The sex-specific associations of carbohydrate eating patterns with hypertension with or without diabetes are shown in \textbf{Table \ref{tab:tab2HYT}}. In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status. Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate with low carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093). 95\% CI of the adjusted OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2. When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively. The negative associations between carbohydrate eating patterns were still observed in women, however, without any statistical evidence in the full adjusted models. \vspace{-0.3cm}

\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex. The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women. As expected, WC increased significantly with the elevated BMI level in both men and women. Strong evidence of differences by obesity level

@@

	\fontsize{8}{11}\selectfont

@@

		Country (\%) &  &  & 0.109 &  &  & 0.631\\
		\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
		\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
		\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
		\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\

@@

were found for age, total energy intake, and carbohydrate intake in both sexes. Specifically, education level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were lower with increasing BMI. Living with partner or not was strongly positively associated with obesity in men but not in women. Men with obesity were found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%). Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed. No difference was found for length of physical activity across obesity levels in men,

@@

@@

		\fontsize{8}{11}\selectfont

@@

			Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
			\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
			\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
			\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
			\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\

@@

while in women, somewhat weak inverse association (\textit{p}=0.038) was confirmed. Interestingly, predefined carbohydrate eating patterns were seemingly not associated with BMI in men (\textit{p} = 0.072) or in women (\textit{p} = 0.253).

Results of the regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}. However, the 95\%CI of the regression coefficients were all too wide and include the null value 0, indicating no statistically supported evidence of the association. But, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes). For women living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI. Compared with women eating low carbohydrate meals, women having a high

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0.43 (-1.13, 0.26) & 0.220\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.820 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
		\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, hypertension, smoking status, total energy}}\\ 
		\multicolumn{6}{l}{{\scriptsize  intake, alcohol consumption.}}\\
	\end{tabular}
\end{table}
\vspace{-0.3cm}
\rowcolors{2}{white}{white}

  carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjusted for age, average household income, education level, smoking status, total energy intake and alcohol consumption. 95\%CI for the adjusted BMI difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001. After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) lower in high carbohydrate eaters versus low carbohydrate eaters on average. On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who live without a partner, although the regression coefficients were not statistically different from 0.

@@

Similarly, when using WC as another measurement of obesity, compared with men who had low carbohydrate eating pattern, only those had a moderate carbohydrate eating pattern were found with about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC in the crude model \textbf{(Table \ref{tab:tab2WC})}. After adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference in men. Again, the interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was found in women in total and without diabetes. Among women who were living with her partner, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) lower WC on average compared with low carbohydrate eaters. The association remained when restricted into non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001). However, for women who lived without a partner, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.043) larger WC compared with low carbohydrate eaters. The evidence for the positive association between moderate carbohydrate eaters and WC was weak and became borderline significant when excluding diabetic women.

>>>>

\textbf{Table \ref{tab:tab1hypetension}} presents the characteristics of men and women participants in the NDNS RP 2008/09-15/16 by hypertension status. The weighted prevalences of hypertension were 30.4\% in men and 27.5\% in women. Among both sexes, there were strong evidence of differences by hypertension status for age, education level, living with a partner or not, smoking status, BMI, abdominal obesity (WC), and prevalence of diabetes (\textit{p} < 0.01). No difference was found among either men or women for ethnicity. Strong evidence of difference was suggested in women for average household income (32741.5 \textsterling/year in non-hypertensive vs. 27862.0 \textsterling/year in hypertensive, \textit{p} < 0.001), and physical activity level (geometric mean: 0.81 hours/day in non-hypertensive compared with 0.53 hours/day in hypertensive, \textit{p} < 0.001) but not in men. Interestingly, in both sexes, hypertensive participants had higher proportion of being classified as low or high carbohydrate eaters; total energy and carbohydrate intake was higher in people with hypertension (\textit{p} < 0.001).

The sex-specific associations of carbohydrate eating patterns with hypertension (both in total and in participants without diabetes) are shown in \textbf{Table \ref{tab:tab2HYT}}. In the crude models, moderate carbohydrate eaters had statistically significant lower odds of having hypertension than low carbohydrate eaters in both men and women irrespective to diabetes status. Among men, after adjustment for selected confounders, which includes: age, live with partner or not, education level, BMI, smoking status, and total energy intake, the odds ratio (OR) comparing moderate with low carbohydrate eaters was 0.68 (95\% CI: 0.43, 1.07) and remained borderline significant (\textit{p} = 0.093). 95\% CI of the adjusted OR became narrower (OR: 0.64, 95\% CI: 0.41, 1.01, \textit{p} = 0.054) when BMI was replaced with WC in model 2. When diabetic men were excluded in the models, the ORs (95\%CI) for moderate and high carbohydrate eaters compared with low carbohydrate eaters were 0.65 (0.41, 1.03) and 0.73 (0.51, 1.06), respectively. The negative associations between moderate carbohydrate eating pattern and hypertension were also observed in women, however, without any statistically significant evidence in the fully adjusted models. High carbohydrate eaters also had lower adjusted odds compared with low carbohydrate eaters, while the 95\% CIs for the adjusted ORs were all wide and included the null value suggesting no evidence of any association in either men or women for high carbohydrate eating pattern and hypertension.

@@

@@

%		Country (\%) &  &  & 0.109 &  &  & 0.631\\
%		\hspace{1em}England & 84.7 (80.9, 87.2) & 85.4 (81.2, 88.8) &  & 84.0 (81.0, 86.6) & 83.5 (79.1, 87.0) & \\
%		\hspace{1em}Northern Ireland & 3.3 (2.2, 4.8) & 1.6 (0.8, 3.1) &  & 2.5 (1.9, 3.5) & 2.6 (1.5, 4.3) & \\
%		\hspace{1em}Scotland & 8.6 (6.3, 11.7) & 7.1 (4.6, 10.9) &  & 8.7 (6.5, 11.7) & 7.9 (5.1, 11.8) & \\
%		\hspace{1em}Wales & 3.9 (2.7, 5.6) & 5.9 (4.0, 8.5) &  & 4.7 (3.7, 6.0) & 6.1 (4.3, 8.6) & \\

@@

@@

\textbf{Table \ref{tab:tab2BMI}} shows the characteristics for participants according to their obesity status stratified by sex. The survey design-weighted prevalence for being overweight and obese in the UK adults were estimated to be 43.4\% and 25.7\% in men, and 30.9\% and 27.4\% in women. Obviously, abdominal obesity (WC) increased significantly with the elevated BMI level in both men and women. Overweight or obese participants were older, having lower total energy intake and lower carbohydrate intake compared with normal weight men and women (\textit{p} < 0.001). Moreover, edu-

@@

		\fontsize{8.5}{11}\selectfont

@@

%			Country (\%) &  &  &  & 0.236 &  &  &  & 0.589\\
%			\hspace{1em}England & 83.9 (79.2, 87.7) & 86.9 (83.6, 89.7) & 81.6 (76.7, 85.7) &  & 84.3 (80.4, 87.5) & 83.7 (79.7, 87.0) & 82.4 (78.2, 85.9) & \\
%			\hspace{1em}Northern Ireland & 3.3 (1.9, 5.8) & 2.3 (1.4, 3.6) & 3.2 (2.0, 4.9) &  & 3.0 (2.1, 4.2) & 2.2 (1.5, 3.2) & 3.4 (2.3, 5.0) & \\
%			\hspace{1em}Scotland & 9.1 (6.1, 13.5) & 6.5 (4.4, 9.7) & 9.0 (5.9, 13.3) &  & 9.0 (6.1, 13.0) & 9.0 (6.3, 12.8) & 8.5 (5.7, 12.6) & \\
%			\hspace{1em}Wales & 3.7 (2.3, 5.8) & 4.3 (3.1, 5.9) & 6.3 (4.0, 9.7) &  & 3.8 (2.9, 5.1) & 5.1 (3.6, 7.2) & 5.7 (4.2, 7.7) & \\

@@

cation level (\textit{p} = 0.022 for men, < 0.001 for women), average household income (\textit{p} = 0.011 for men, < 0.001 for women) were decreasing with increasing BMI. Living with partner or not was strongly positively associated with obesity in men but not in women. Men with obesity were also found to have the lowest proportion of never being a smoker (47.9 \%), and the highest proportion of being ex-smoker (32.9\%). Association between smoking status and obesity in women was only with very weak evidence (\textit{p} = 0.042) but similar pattern as in men was also observed (higher proportion of ex- and current smokers in overweight or obese women). No difference was found for length of physical activity across obesity levels in men, while in women, somewhat weak inverse association (\textit{p}=0.038) was confirmed. Interestingly, predefined carbohydrate eating patterns were seemingly not associated with BMI in men (\textit{p} = 0.072) or in women (\textit{p} = 0.253).

@@

	\caption{\label{tab:tab2BMI}Associations of carbohydrate eating patterns with BMI in the UK adults, with or without diabetes. \\ (NDNS RP 2008/09-15/16, sample size = 6155)}\vspace{-0.3cm}
	\centering
	\fontsize{9}{11}\selectfont
	\begin{tabular}[t]{lccccc}
		\hiderowcolors
		\toprule
		\multicolumn{1}{c}{ } & \multicolumn{5}{c}{\textbf{Carbohydrate eating patterns}} \\
		\cmidrule(l{2pt}r{2pt}){2-6}
		\textbf{Model} & \textbf{Low} & \textbf{Moderate} & \textbf{\textit{P} value\textsuperscript{*}} & \textbf{High} & \textbf{\textit{P} value\textsuperscript{*}}\\
		\midrule
		\showrowcolors
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Men (n = 2537)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.78 (-1.62, 0.06) & 0.068 & -0.28 (-0.96, 0.41) & 0.426\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.20 (-1.06, 0.66) & 0.654 & -0.43 (-1.13, 0.26) & 0.220\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.65 (-1.49, 0.19) & 0.127 & -0.21 (-0.89, 0.48) & 0.557\\
		\hspace{1em}\hspace{1em}Model 1\textsuperscript{\dag} & -- & -0.10 (-0.97, 0.77) & 0.820 & -0.39 (-1.10, 0.31) & 0.269\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\textbf{Women (n = 3618)}}\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.30 (-1.18, 0.57) & 0.496 & -0.76 (-1.44, -0.82) & 0.028\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.93 (-2.33, 0.46) & 0.188 & -1.76 (-2.78, -0.73) & 0.001\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.17 (-0.35, 2.70) & 0.132 & 0.57 (-0.58, 1.719 & 0.332\\
		\addlinespace[0.3em]
		\multicolumn{6}{l}{\hspace{1em}\textbf{BMI in non-diabetics}}\\
		\hspace{1em}\hspace{1em}Crude model & -- & -0.24 (-1.12, 0.65) & 0.601 & -0.71 (-1.39, -0.03) & 0.040\\
		\hspace{1em}\hspace{1em}Live with partner\textsuperscript{\ddag} & -- & -0.86 (-2.28, 0.55) & 0.232 & -1.62 (-2.65, -0.58) & 0.002\\
		\hspace{1em}\hspace{1em}Live alone\textsuperscript{\ddag} & -- & 1.22 (-0.34, 2.78) & 0.124 & 0.43 (-0.71, 1.56) & 0.462\\
%		\bottomrule \\
    	\bottomrule
		\multicolumn{6}{l}{{\scriptsize \textit{Note: }}}\\
		\multicolumn{6}{l}{{\scriptsize \textbf{Abbreviations}: BMI body mass index; NDNS RP, national dietary and nutrition survey rolling programme.}}\\
		\multicolumn{6}{l}{{\scriptsize Diabetes was defined by A1C > 6.5\%.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{*} \textit{P} values were obtained from wald tests from linear regression models.}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\dag} Adjusted for age, live with partner or not, education level, hypertension (yes or no), smoking status, total }}\\
		\multicolumn{6}{l}{{\scriptsize  energy intake, alcohol consumption;}}\\
		\multicolumn{6}{l}{{\scriptsize \textsuperscript{\ddag} Adjusted for age, average household income, education level, hypertension, smoking status, total energy}}\\ 
		\multicolumn{6}{l}{{\scriptsize  intake, alcohol consumption.}}\\
	\end{tabular}
\end{table}

Results of the multivariable linear regression analyses showed inverse associations between latent classes of carbohydrate eating patterns and BMI among men \textbf{(Table \ref{tab:tab2BMI})}. However, the 95\%CI of the regression coefficients were all wide and included the null value 0, indicating no statistically supported evidence for the inverse association. However, evidence of interaction effect was found in whether live with a partner or not on the association between carbohydrate eating patterns and BMI (\textit{p} for interaction = 0.014 and 0.036 for women in total and without diabetes). For women who were living with her partner, latent classes of carbohydrate eating patterns were negatively associated with BMI. Compared with women eating low carbohydrate food pattern, women having a high carbohydrate eating pattern were averagely associated with 1.76 kg/m\textsuperscript{2} lower BMI after adjustment of age, average household income, education level, smoking status, total energy intake and alcohol consumption. 95\%CI for the adjusted BMI difference was 0.73 to 2.78 kg/m\textsuperscript{2}, \textit{p} = 0.001. After excluding diabetic women, BMI was still 1.62 kg/m\textsuperscript{2} (95\%CI: 0.58, 2.65, \textit{p} = 0.002) smaller in high carbohydrate eaters versus low carbohydrate eaters on average. On the contrary, latent classes of carbohydrate eating patterns were positively associated with BMI in women who were living by themselves, although the regression coefficients were not statistically different from 0.

Similarly, when looking at the association between carbohydrate eating pattern and abdominal obesity (WC), men who were classified as moderate carbohydrate eaters were found to had about 3 cm (95\%CI: 0.52, 5.49 cm, \textit{p} = 0.018) smaller WC compared with low carbohydrate eaters in the crude model \textbf{(Table \ref{tab:tab2WC})}. However, after adjustment of age, living with partner or not, average household income, education level, hypertension, smoking status, total energy intake, and alcohol consumption, the association attenuated to no difference. The interaction effect of whether living with partner or not on the association between carbohydrate eating patterns and WC was again found in women in total and without diabetes. Among women who were living with their partners, high carbohydrate eaters had 4.71 cm (95\%CI: 2.43, 7.00, \textit{p} < 0.001) smaller WC on average compared with low carbohydrate eaters. The association remained when restricted the sample to non-diabetic women (-3.74 cm, 95\% CI: -5.97, -1.51,  \textit{p} = 0.001). However, for women who were living alone, moderate carbohydrate eaters had 3.17 cm (95\%CI: 0.05, 6.30, \textit{p} = 0.047) larger WC on average compared with low carbohydrate eaters. The evidence for the positive association between moderate carbohydrate eaters and WC in women became weaker but with borderline significant when excluding diabetic women (3.08 cm, 95\%CI: -0.09, 6.25, \textit{p} = 0.057).

@@

### 2018-08-16 paper/Chapters/Chapter4.tex
results with survery regression updated

Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters at night, they consumed the highest amount of energy, especially during time period as late as after 10 pm. People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than the other two types of carbohydrate eaters. They consumed the highest amount of carbohydrates and also total energy during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am. These individuals in the NDNS RP were younger, mostly single, with lower average income, and lower education level. They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, Mansukhani2018}.

>>>>

Next, when looking into the details of the timing and composition of the energy intake among the moderate carbohydrate eaters, we realised that although these individuals did not consume as much alcohol as low carbohydrate eaters at night, they consumed the highest amount of energy, especially during time period as late as after 10 pm. People fell into moderate carbohydrate eaters group seemed to have the tendency of having their food or meals later than the other two types of carbohydrate eaters. They consumed the highest amount of carbohydrates and also total energy among three types of carbohydrate eaters during the following time slots: 9-12 noon, 2-5 pm, 8-10 pm, and 10pm-6am. These individuals in the NDNS RP were younger, mostly single, with lower average income, and lower education level. They might possibly correspond to the "late eaters" defined by previous studies \parencite{leech2017temporal, mansukhani2018investigating}.

### 2018-08-16 paper/main.tex
results with survery regression updated

\subject{Medical Statistics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{https://www.lshtm.ac.uk/}{London School of Hygiene and Tropical Medicine}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{}{Page count: XX from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{Candidate number: 110765} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

>>>>

\subject{Medical Statistics} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{https://www.lshtm.ac.uk/}{London School of Hygiene and Tropical Medicine}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{}{Page count: 42 from Introduction to Conclusions}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
\group{Candidate number: 110765} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://faculty.university.com}{Faculty Name}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
